---
title: "Module8_Project"
author: "Will Brewster"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Project Update #1:

We have selected the research topic #2, which will use the data on the sales of liquors in Iowa. At this point we will focus on research question #3 (Do geographies with higher median consume more alcohol in total?). A GitHub repository has been created (Group-2-Project-Option-2.3).
So far, below is an initial data summary of the geographies, alcohol consumption, and population: 
```{r}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(readr)

project_acs_counties <- read_csv("project.acs.counties.csv")
project_acs_counties1 <- project_acs_counties |> 
  select(county, income)

#Top 5 counties by income:
head(arrange(project_acs_counties1, desc(income)),5)

#Bottom counties by income: 
head(arrange(project_acs_counties1, (income)),5)


project_sales_counties1 <- project_sales_counties <- read_csv("project.sales.counties.csv")

#Summary of total county sales:
project_sales_counties2 <- project_sales_counties1 |> 
  group_by(county) |> 
  summarize(sales = sum(sale.dollars)) |> 
  arrange(desc(sales))

#joining data sets: 
combined <- project_acs_counties1 |> 
  left_join(project_sales_counties2)

arrange(combined, desc(income))
arrange(combined, income)

plot1 <- 
  ggplot(combined, aes(x = income, y = sales)) +
  geom_point()
plot1


```
